\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2019-08-23 icse/impl.tex
First draft
Updated number in implementation

\paragraph{Inessential Built-in Objects}
JavaScript provides various standard built-in objects to support
helper functions.  However, several built-in libraries are not essential
to the core JavaScript semantics but support extra functionalities such as
\( \code{Math} \), \( \code{Date} \), \( \code{RegExp} \), and
\( \code{JSON} \).  Thus, we decided not to support such libraries
following the tradition of KJS~\cite{kjs}.

\subsection{Compile Rules for ECMAScript}
\begin{table}[t]
  \centering
  \caption{Compile rules in ECMAScript 2020}
  \label{table:rules}
\vspace*{-1em}
  \[
    \begin{array}{c?r|r|r|r|r|r|r}
      \text{Name}
      & \multicolumn{1}{c|}{\code{Stmt}}
      & \multicolumn{1}{c|}{\code{Expr}}
      & \multicolumn{1}{c|}{\code{Cond}}
      & \multicolumn{1}{c|}{\code{Value}}
      & \multicolumn{1}{c|}{\code{Ty}}
      & \multicolumn{1}{c|}{\code{Ref}}
      & \multicolumn{1}{c}{\code{SecNo}}\\\hline
      \text{\# Rules}
      & \inred{XX}
      & \inred{XX}
      & \inred{XX}
      & \inred{XX}
      & \inred{XX}
      & \inred{XX}
      & \inred{XX}
    \end{array}
  \]
\end{table}

>>>>

\paragraph{Inessential Built-in Objects}
JavaScript provides various standard built-in objects to support
helper functions.  However, several built-in libraries are not essential
to the core JavaScript semantics but support extra functionalities such as
\( \code{Math} \), \( \code{Date} \), \( \code{RegExp} \), and
\( \code{JSON} \).  Thus, we decided not to support such libraries
following the tradition of KJS~\cite{kjs}, which is a complete
formal semantics of JavaScript.

\subsection{Compile Rules for ECMAScript}
\begin{table}[t]
  \centering
  \caption{Compile rules in ECMAScript 2020}
  \label{table:rules}
\vspace*{-1em}
  \[
    \begin{array}{c?r|r|r|r|r|r|r}
      \text{Name}
      & \multicolumn{1}{c|}{\code{Stmt}}
      & \multicolumn{1}{c|}{\code{Expr}}
      & \multicolumn{1}{c|}{\code{Cond}}
      & \multicolumn{1}{c|}{\code{Value}}
      & \multicolumn{1}{c|}{\code{Ty}}
      & \multicolumn{1}{c|}{\code{Ref}}
      & \multicolumn{1}{c}{\code{SecNo}}\\\hline
      \text{\# Rules}
      & 17
      & 16
      & 8
      & 11
      & 33
      & 7
      & 21
    \end{array}
  \]
\end{table}
